### 2018-04-16 vipassana-for-hackers.tex
bump version
spelling
practices spelling
s/practies/practices/

\begin{titlepage}
   \vspace*{\stretch{1.0}}
   \begin{center}
     \Huge\textbf{Vipassana for Hackers}\\
     \vspace{5cm}
     \large\textit{Steven Deobald}\\
     \large\textit{Version 1.4}\\
     \large\textit\today
   \end{center}
   \vspace*{\stretch{2.0}}
\end{titlepage}

@@

At the end of the first day of a 10-day Vipassana course, the breath is described as a bridge ``from the known to the unknown, because respiration is one function of the body that can be either conscious or unconscious, intentional or automatic.'' During the 3-day Anapana session of a 10-day course, students are instructed to \textit{consciously} direct attention toward their breath -- and even gently control the breath for brief periods to maintain attention when the mind won't stop wandering -- until awareness of breath, without force, lasts for extended periods. Given that the breath is the one function of the body which operates both consciously and unconsciously, it makes sense that it acts as the starting point for many meditation practies, including Vipassana. The intention of Vipassana is to train the mind out of habits and tendencies which have embedded themselves into the brain and nervous system at an unconscious level. To do this, one must first learn to access one's unconscious. Through the breath, Anapana meditation fulfills this purpose.

>>>>

\begin{titlepage}
   \vspace*{\stretch{1.0}}
   \begin{center}
     \Huge\textbf{Vipassana for Hackers}\\
     \vspace{5cm}
     \large\textit{Steven Deobald}\\
     \large\textit{Version 1.5}\\
     \large\textit\today
   \end{center}
   \vspace*{\stretch{2.0}}
\end{titlepage}

@@

At the end of the first day of a 10-day Vipassana course, the breath is described as a bridge ``from the known to the unknown, because respiration is one function of the body that can be either conscious or unconscious, intentional or automatic.'' During the 3-day Anapana session of a 10-day course, students are instructed to \textit{consciously} direct attention toward their breath -- and even gently control the breath for brief periods to maintain attention when the mind won't stop wandering -- until awareness of breath, without force, lasts for extended periods. Given that the breath is the one function of the body which operates both consciously and unconsciously, it makes sense that it acts as the starting point for many meditation practices, including Vipassana. The intention of Vipassana is to train the mind out of habits and tendencies which have embedded themselves into the brain and nervous system at an unconscious level. To do this, one must first learn to access one's unconscious. Through the breath, Anapana meditation fulfills this purpose.
